Spectral Experts for Estimating Mixtures of Linear Regressions

### 2013-06-13 doc/icml-presentation/presentation.tex
Added lots of pretty graphs and improved the presentation quatlity.

\usepackage{tikz}
\usepackage[debug]{scabby}
%\usepackage{scabby}

@@

  \splitcolumn{%
    \begin{itemize} 
      \item  \tikzmark{gen} {\bf Generative Models}
        \uncover<2->{%
        \begin{itemize}
          \item Gaussian Mixture Models
          \item Hidden Markov Models
          \item Latent Dirichlet Allocation
          \item PCFGs
          \item \dots
        \end{itemize}
        }
      \item<3-> \tikzmark{disc} {\bf Discriminative Models} 
        \uncover<4->{%
        \begin{itemize}
          \item Mixture of Experts
          \item Latent CRFs
          \item Discriminative LDA
          \item \dots
        \end{itemize}
        }
      \item<4-> {\em Easy to include features and tend to be more accurate.}
      \end{itemize}
  }{%
  \begin{canvas}
    \point{mark}{(3cm,0)};
    \point{gen}{({pic cs:gen} -| mark)}
    \point{disc}{({pic cs:disc} -| mark)}
    \drawgen<1->{($(gen) + (0,1.5cm)$)};
    \drawdisc<3->{($(disc) + (0,0.0cm)$)};
  \end{canvas}
  }

@@

  \begin{tikzpicture}
    % x, y
    \node at (0,0) {%
    \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood.png}
    \includegraphics<2>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mle.png}
    \includegraphics<3>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-em.png}
    \includegraphics<4>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom.png}
      };
    %\point{opt}{(0.4cm,-1.1cm)};
    %\node[style=lbl,below=0.0cm of opt,scale=1.2] {$\hlmath{blue}{\theta^*}$};
    % Axes
    \draw[-latex] (-6cm,-2.25cm) -- node[right,at end]{$-\log(p_{\theta}(x))$}  (-6cm,2cm);
    \draw[-latex] (-6cm,-2.25cm) -- node[above,at end]{$\theta$}  (5cm,-2.25cm);
  \end{tikzpicture}

@@

\begin{frame}
  \frametitle{Aside: Tensor Operations}
  \splitcolumn{%
    \begin{itemize}
      \item \tikzmark{tensoring} Tensoring
        $$x\tp{3}_{ijk} = x_i x_j x_k$$
      \item<2-> \tikzmark{innerp}Inner product
        \begin{align*}
          \innerp{A}{B} &= \sum_{ijk} A_{ijk} B_{ijk} \\
          \uncover<3->{%
            &= \innerp{\vvec{A}}{\vvec{B}} 
          }
        \end{align*}
    \end{itemize}
  }{%
  }
  \begin{canvas}
    \point{mark}{(6.8cm,0)};
    % Tensoring
    \tikzcube{tensoring}{black,fill=white}{($({pic cs:tensoring} -| mark) + (0,0,0)$)}{1}{1}{1};
    \node at ($(tensoring) + (1.0cm,-0.3cm)$) {$=$};
    \tikzcube{v1}{black,fill=white}{($(tensoring) + (2.5cm,-0.3cm)$)}{1}{0.3}{0.3};
    \node (lbl1) at ($(v1) + (0.40cm,-0.1cm)$) {$\times$};
    \tikzcube{v2}{black,fill=white}{($(v1) + (1cm,0.3cm)$)}{0.3}{1}{0.3};
    \node at ($(lbl1) + (1cm,0.0cm)$) {$\times$};
    \tikzcube{v3}{black,fill=white}{($(v2) + (1cm,-0.3cm)$)}{0.3}{0.3}{1};

    % Inner product
    \uncover<2->{%
    \point{ptA}{($({pic cs:innerp} -| mark) + (0,0.2cm)$)}
    \point{ptB}{($(ptA) + (2cm,0)$)}
    \tikzcube{innerpA}{black,fill=yellow}{($(ptA) + (0,0,0)$)}{1}{1}{1};
    \tikzcube{innerpB}{black,fill=blue,opacity=0.7}{($(ptB) + (0,0,0)$)}{1}{1}{1};
    \node[scale=2.0] (op1a) at ($(ptA) + (-1.3cm,-0.3cm)$) {$\langle$};
    \node (op1b) at ($(ptA) + (0.7cm,-0.3cm)$) {$,$};
    \node[scale=2.0] (op1c) at ($(ptB) + (0.8cm,-0.3cm)$) {$\rangle$};
    \node[scale=1.0] (op2) at ($(op1c) + (1.5cm,0.0cm)$) {$= \mathmg{0.5}$};
    }

    % Inner product 2
    \uncover<3->{%
    \tikzrect{innerpAv}{black,fill=yellow}{($(ptA) + (0,-1.5cm)$)}{0.3}{2.0};
    \tikzrect{innerpBv}{black,fill=blue,opacity=0.7}{($(ptB) + (0,-1.5cm)$)}{0.3}{2.0};
    \node[scale=2.0] (op1a) at ($(innerpAv) + (-1.3cm,-1.1cm)$) {$\langle$};
    \node (op1b) at ($(innerpAv) + (0.7cm,-1.1cm)$) {$,$};
    \node[scale=2.0] (op1c) at ($(innerpBv) + (0.8cm,-1.1cm)$) {$\rangle$};
    \node[scale=1.0] (op2) at ($(op1c) + (1.5cm,0.0cm)$) {$= \mathmg{0.5}$};
    }
  \end{canvas}

@@

\begin{frame}
  \frametitle{Example: Gaussian Mixture Model}

  \splitcolumn{%
    \begin{itemize}
      \item Generative process\tikzmark{gen}:
      \begin{align*}
        h &\sim \Mult([\pi_1, \pi_2, \cdots, \pi_k]) \\
        x &\sim \normal{\beta_h}{\sigma^2}.
      \end{align*}
      \item Moments:
      \begin{align*}
          \uncover<2->{%
          \E[x|h] &= \beta_h \\
          }
          \uncover<3->{%
          \E[x] &= \sum_h \pi_h \beta_h \\
          }
          \uncover<4->{%
          \tikzmark{m2}
          \E[x\tp{2}] &= \sum_h \pi_h (\beta_h \beta_h^T) \\
                      &= \sum_h \pi_h \beta_h{\tp{2}} \\
                      }
          \uncover<5->{%
          \tikzmark{m3}
          \E[x\tp{3}] &= \sum_h \pi_h \beta_h\tp{3}.
          }
        \end{align*}
    \end{itemize}
  }{%
  }
  \begin{canvas}
    % The model
    \point{mark}{(6.5cm,0)};
    \point{start}{({pic cs:gen} -| mark)};
    \drawgen{($(start) + (0,2cm)$)};
    %\node[anchor=west] (diag1) at ($(start)$) {%
    %  \includegraphics[width=0.45\textwidth,height=2cm,keepaspectratio]{figures/gen.png}
    %};
    \node[anchor=west] (diag) at ($(start) + (1cm,1.0cm)$) {%
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/mog.png}
    };

    \uncover<4->{%
      \point{m2}{({pic cs:m2} -| mark)};
      \tikzrect{M2}{black,fill=white}{($(m2) + (1cm,1cm)$)}{1}{1};
      \node[anchor=west] at ($(m2) + (1.1cm, 0.5cm)$) {$\E[x\tp{2}]$};
      \node[anchor=east] at ($(m2) + (-0.1cm, 0.5cm)$) {$d$};
      \node[anchor=south] at ($(m2) + (0.5cm, 1.0cm)$) {$d$};
    }
    \uncover<5->{%
      \point{m3}{($({pic cs:m3} -| mark) + (1cm,1cm)$)};
      \tikzcube{M3}{black,fill=white}{($(m3) + (0,0,0)$)}{1}{1}{1};
      \node[anchor=west] at ($(m3) + (0.5cm, -0.5cm)$) {$\E[x\tp{3}]$};
      \node[anchor=east] at ($(m3) + (-1.1cm, -0.5cm)$) {$d$};
    }
  \end{canvas}

@@

\begin{frame}
  \frametitle{Solution: Tensor Factorization}
  \cornertext<3->{\cite{AnandkumarGeHsu2012}}

  \splitcolumn{%
    \begin{itemize}
      \item \tikzmark{gen}$\E[x\tp{3}] = \sum_{h=1}^k \pi_h \beta_h\tp{3}$.
      \item<3-> If $\beta_h$ are orthogonal, the are eigenvectors!
        \begin{align*}
          \E[x\tp{3}](\beta_h,\beta_h) 
            %&= \sum_{h'=1}^k \pi_{h'} (\beta_{h}^T \beta_{h'})^2 \beta_{h'} \\
            %&= \sum_{h'=1}^k \pi_{h'} \delta_{hh'} \beta_{h'} \\
            &= \pi_{h} \beta_{h}.
        \end{align*}
      \item<4-> In general, whiten $\E[x\tp{3}]$ first.
    \end{itemize}
  }{%
  }
  \begin{canvas}
    \point{mark}{(6.5cm,0)};
    \point{start}{({pic cs:gen} -| mark)};

    \drawgen{($(start) + (0,2cm)$)};
    \node[anchor=west] (diag) at ($(start) + (1cm,0.0cm)$) {%
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/mog.png}
    };
    \uncover<2->{%
      \tensorfactorization{(2cm,-1cm)};
    }
  \end{canvas}
\end{frame}

@@

  \begin{canvas}
    % Tasks.
    \drawgen{(3cm,0)}
    \node[below=0.1cm of x.south] {Generative Models};

    % Highlight
    \draw[scale=0.8,fill=green,opacity=0.4,dashed] (8cm,1cm) rectangle (14cm,-4cm);
      \drawdisc{(9cm,0)}
      \node[below=0.1cm of y.south] {Discriminative Models};

@@

  \splitcolumn{%
    \tikzmark{model}
    \begin{tikzpicture}
      \drawdisc{(0,0)}
    \end{tikzpicture}
    \begin{itemize}
      \item<2-> $h \sim \Mult([\pi_1, \pi_2, \cdots, \pi_k])$.
      \item<4-> $y = \beta_h^T x + \epsilon$.
    \end{itemize}
  }{%
  }
    \begin{canvas}
      % x, y
      \point{mark}{(5.5cm,0)}
      \point{model}{({pic cs:model} -| mark)}
      \node[anchor=west] at ($(model) + (0,0.5cm)$) {%
      \includegraphics<1>[width=5cm,height=6cm,keepaspectratio]{figures/mlr-data-2.png}
      \includegraphics<2>[width=5cm,height=6cm,keepaspectratio]{figures/mlr-data-3a.png}
      \includegraphics<3>[width=5cm,height=6cm,keepaspectratio]{figures/mlr-data-3b.png}
      \includegraphics<4>[width=5cm,height=6cm,keepaspectratio]{figures/mlr-data-4a.png}
      \includegraphics<5>[width=5cm,height=6cm,keepaspectratio]{figures/mlr-data-4b.png}
      %\includegraphics<6>[width54cm,height=6cm,keepaspectratio]{figures/mlr-data-4c.png}
      \includegraphics<6>[width=5cm,height=6cm,keepaspectratio]{figures/mlr-data-5.png}
      \includegraphics<7>[width=5cm,height=6cm,keepaspectratio]{figures/mlr-data-6.png}
        };
    \end{canvas}
\end{frame}

@@

  \begin{canvas}
    \node[anchor=west] (data) at (0,0) {%
    \includegraphics[width=4cm,height=6cm,keepaspectratio]{figures/mlr-data.png}
    };

    % x, y
    \node[anchor=west,scale=1.0] (params) at (7cm,0) {%
      $\begin{bmatrix} \pi_1 \\ \pi_2 \\ \vdots \\ \pi_k \end{bmatrix}  
       \begin{bmatrix} 
                 &         &       &         \\
                 &         &       &         \\
         \beta_1 & \beta_2 & \dots & \beta_k \\
                 &         &       &         \\
                 &         &       &         
       \end{bmatrix} $
      };
    %\node[anchor=west,right=0.1cm of params] {%
    %\includegraphics[width=4cm,height=2cm,keepaspectratio]{figures/disc.png}
    %};

@@

  \splitcolumn{%
  \begin{align*}
    \action<1->{%
    y &= \mathmb{\ob{\innerp{\E[\beta_h]}{x}}^{\textrm{linear measurement}}} &&+ \mathmr{\ob{(\beta_h - \E[\beta_h])^T x + \epsilon}^{\textrm{noise}}} \\[4ex]
    }
    \action<2->{%
      y^2 
      &= \left(\innerp{\beta_h}{x} + \epsilon\right)^2 && \\
    }
    \action<3->{%
    &= 
    \color{blue}
      \robustaltm<3>{%
            \innerp{\E[\beta_h\tp{2}]}{x\tp{2}}
        }{%
          \ub{\innerp{\E[\beta_h\tp{2}]}{x\tp{2}}}_{M_2} 
        }
        &&+ \color{DarkGreen} \textrm{bias} + \color{red} \textrm{noise} \\[4ex]
    }
    \action<5->{%
    y^3 &= \color{blue} \ub{\innerp{\E[\beta_h\tp{3}]}{x\tp{3}}}_{M_3} &&+ \color{DarkGreen} \textrm{bias} + \color{red} \textrm{noise} 
    }
  \end{align*}
  }{%
  }

@@

\begin{frame}
  \frametitle{Method of Moments for the Mixture of Linear Regressions.}
  \centering

@@

  \begin{canvas}
    \uncover<2->{%
      \tensorfactorization{(-3cm,-1cm)};
    }
  \end{canvas}

@@

    \begin{align*}
      \hat M_{\robustaltm<-2>{2}{\mathmb{3}}} &= \arg\min_{M} \sum_{(x,y)\in\mathcal{D}} \left(y^2 - 
      \robustaltm<-2>{\innerp{M_2}{x\tp{2}}}{\mathmb{\innerp{M_3}{x\tp{3}}}}
      - \textrm{bias}\right)^2 
      \uncover<2->{+
      \robustaltm<2>{\mathmb{\ub{\|M\|_{*}}_{\sum_i \sigma_i(M)}}}
        {\|M\|_{*}}
      } \\
    \end{align*}

  \begin{canvas}
    % x, y
    \alt<-2>{%
      \matrixfactorization{(2cm,0)}
    }{%
      \tensorfactorization{(2cm,0)}
    }
  \end{canvas}
\end{frame}

@@

  \begin{canvas}
    % x, y
    \node[anchor=west] (em) at (-0.5cm,-1.5cm) {%
      \includegraphics<1>[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3.png}
      \includegraphics<2>[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3-em.png}
      \includegraphics<3>[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3-spec.png}
      \includegraphics<4->[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3-specm.png}
      };
    % x, y
    \node[anchor=west, right=6cm of em] at (em.west) {%
      \includegraphics[width=\textwidth,height=5cm,keepaspectratio]{figures/hist.png}
    };

@@

  \begin{tikzpicture}
    \node at (0,0) {%
      \includegraphics<1>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom.png}
      \includegraphics<2>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom-em1.png}
      \includegraphics<3>[width=\textwidth,height=6cm,keepaspectratio]{figures/likelihood-mom-em2.png}
    };
    \draw[-latex] (-6cm,-2.25cm) -- node[right,at end]{$-\log(p_{\theta}(x))$}  (-6cm,2cm);
    \draw[-latex] (-6cm,-2.25cm) -- node[above,at end]{$\theta$}  (5cm,-2.25cm);

    \node<2-> at (1.8cm,0.6cm) {$\hlmath{DarkGreen}{\theta_{spec}}$};
    \node<3-> at (0.3cm,-0.8cm) {$\hlmath{blue}{\theta^{*}}$};
  \end{tikzpicture}

>>>>

\usepackage{tikz}
%\usepackage[debug,debugmarks]{scabby}
\usepackage{scabby}

@@

  \splitcolumn{%
    \begin{itemize} 
      \item  \tikzmark{gen} {\bf Generative Models}
        \uncover<2->{%
        \begin{itemize}
          \item Gaussian Mixture Models
          \item Hidden Markov Models
          \item Latent Dirichlet Allocation
          \item PCFGs
          \item \dots
        \end{itemize}
        }
      \item<3-> \tikzmark{disc} {\bf Discriminative Models} 
        \uncover<4->{%
        \begin{itemize}
          \item Mixture of Experts
          \item Latent CRFs
          \item Discriminative LDA
          \item \dots
        \end{itemize}
        }
      \item<5-> {\em Easy to include features and tend to be more accurate.}
      \end{itemize}
  }{%
  \begin{canvas}
    \point{mark}{(3cm,0)};
    \point{gen}{({pic cs:gen} -| mark)}
    \point{disc}{({pic cs:disc} -| mark)}
    \drawgen<1->{($(gen) + (0,0.0cm)$)};
    \drawdisc<3->{($(disc) + (0,-0.5cm)$)};
  \end{canvas}
  }

@@

  \begin{tikzpicture}
    % x, y
    \llhood{0}{0};
    \node[scale=0.7] at (mle) {x};
    \node<2-> at ($(mle) + (0.6cm,0)$) {$\mathmb{\theta^*_{\textrm{MLE}}}$};
    \node[scale=0.7] at (em1) {x};
    \node<3-> at ($(em1) + (0.5cm,0)$) {$\mathmr{\hat\theta_{\textrm{EM}}}$};
    \node[scale=0.7] at (em2) {x};
    \node<3-> at ($(em2) + (0.5cm,0)$) {$\mathmr{\hat\theta_{\textrm{EM}}}$};

    \draw<4->[latex-latex,DarkGreen,line width=1pt] ($(mle) + (-0.8cm,0.8cm)$) -- node[above]{$\mathmg{\epsilon}$} ($(mle) + (+0.8cm,0.8cm)$);
  \end{tikzpicture}

@@

\begin{frame}
  \frametitle{Aside: Tensor Operations}
  \splitcolumn{%
    \begin{itemize}
      \item \tikzmark{tensoring} Tensoring
        $$x\tp{3}_{ijk} = x_i x_j x_k$$
      \item<2-> \tikzmark{innerp}Inner product
        \begin{align*}
          \innerp{A}{B} &= \sum_{ijk} A_{ijk} B_{ijk} \\
          \uncover<3->{%
            &= \innerp{\vvec{A}}{\vvec{B}} 
          }
        \end{align*}
    \end{itemize}
  }{%
  }
  \begin{canvas}
    \point{mark}{(1.0cm,0)};
    \point{tensoring-pos}{({pic cs:tensoring} -| mark)}
    % Tensoring
    \tikzcube{tensoring}{black,fill=white}{($(tensoring-pos) + (0,-3cm) + (0,0,0)$)}{1}{1}{1};
    \node at ($(tensoring) + (1.0cm,-0.3cm)$) {$=$};
    \tikzcube{v1}{black,fill=white}{($(tensoring) + (2.5cm,-0.3cm)$)}{1}{0.3}{0.3};
    \node (lbl1) at ($(v1) + (0.40cm,-0.1cm)$) {$\times$};
    \tikzcube{v2}{black,fill=white}{($(v1) + (1cm,0.3cm)$)}{0.3}{1}{0.3};
    \node at ($(lbl1) + (1cm,0.0cm)$) {$\times$};
    \tikzcube{v3}{black,fill=white}{($(v2) + (1cm,-0.3cm)$)}{0.3}{0.3}{1};

    % Inner product
    \uncover<2->{%
    \point{ptA}{($({pic cs:innerp} -| mark) + (0,-3.0cm)$)}
    \point{ptB}{($(ptA) + (2cm,0)$)}

    \tikzcube{innerpA}{black,fill=yellow}{($(ptA) + (0,0,0)$)}{1}{1}{1};
    \tikzcube{innerpB}{black,fill=blue!70}{($(ptB) + (0,0,0)$)}{1}{1}{1};

    \innerpdiagt{(ptA)}{(ptB)};
    \node[scale=1.0] at ($(ptB) + (1.5cm,-0.3cm)$) {$= \mathmg{0.5}$};
    }

    % Inner product 2
    \uncover<3->{%
    \point{ptvA}{($(ptA) + (0,-2cm)$)}
    \point{ptvB}{($(ptB) + (0,-2cm)$)}

    \tikzrect{innerpAv}{black,fill=yellow}{($(ptvA) + (0,0.5cm)$)}{0.3}{2.0};
    \tikzrect{innerpBv}{black,fill=blue!70}{($(ptvB) + (0,0.5cm)$)}{0.3}{2.0};

    \innerpdiagt{(ptvA)}{(ptvB)};
    \node[scale=1.0] at ($(ptvB) + (1.5cm,-0.3cm)$) {$= \mathmg{0.5}$};
    }
  \end{canvas}

@@

\begin{frame}
  \frametitle{Example: Gaussian Mixture Model}
  \splitcolumn{%
    \begin{itemize}
      \item Generative process\tikzmark{gen}:
      \begin{align*}
        h &\sim \Mult([\pi_1, \pi_2, \cdots, \pi_k]) \\
        x &\sim \normal{\beta_h}{\sigma^2}.
      \end{align*}
      \item Moments:
      \begin{align*}
          \uncover<2->{%
          \E[x|h] &= \beta_h \\
          }
          \uncover<3->{%
          \E[x] &= \sum_h \pi_h \beta_h \\
          }
          \uncover<4->{%
          \tikzmark{m2}
          \E[x\tp{2}] &= \sum_h \pi_h (\beta_h \beta_h^T) \\
                      &= \sum_h \pi_h \beta_h{\tp{2}} \\
                      }
          \uncover<5->{%
          \tikzmark{m3}
          \E[x\tp{3}] &= \sum_h \pi_h \beta_h\tp{3}.
          }
        \end{align*}
    \end{itemize}
  }{%
  }
  \begin{canvas}
    % The model
    \point{mark}{(1cm,0)};
    \point{start}{(1cm,1cm)}; %{pic cs:gen} -| mark)};
    \drawgen{($(start) + (0,1cm)$)};
    %\node[anchor=west] (diag1) at ($(start)$) {%
    %  \includegraphics[width=0.45\textwidth,height=2cm,keepaspectratio]{figures/gen.png}
    %};
    \node[anchor=west] (diag) at ($(start) + (1cm,0.0cm)$) {%
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/mog.pdf}
    };

    \uncover<4->{%
      \point{m2-pos}{({pic cs:m2} -| mark)};
      \point{m2}{($(m2-pos) - (0,4.5cm)$)};
      \tikzrect{M2}{black,fill=white}{($(m2) + (1cm,1cm)$)}{1}{1};
      \node[anchor=west] at ($(m2) + (1.1cm, 0.5cm)$) {$\E[x\tp{2}]$};
      \node[anchor=east] at ($(m2) + (-0.1cm, 0.5cm)$) {$d$};
      \node[anchor=south] at ($(m2) + (0.5cm, 1.0cm)$) {$d$};
    }
    \uncover<5->{%
      \point{m3-pos}{({pic cs:m3} -| mark)};
      \point{m3}{($(m3-pos) - (-1cm,3.5cm)$)};
      \tikzcube{M3}{black,fill=white}{($(m3) + (0,0,0)$)}{1}{1}{1};
      \node[anchor=west] at ($(m3) + (0.5cm, -0.5cm)$) {$\E[x\tp{3}]$};
      \node[anchor=east] at ($(m3) + (-1.1cm, -0.5cm)$) {$d$};
    }
  \end{canvas}

@@

\begin{frame}[t]
  \frametitle{Solution: Tensor Factorization}
  \cornertext<3->{\cite{AnandkumarGeHsu2012}}

  \splitcolumn{%
    \begin{itemize}
      \item \tikzmark{gen}$\E[x\tp{3}] = \sum_{h=1}^k \pi_h \beta_h\tp{3}$.
      \item<3-> If $\beta_h$ are orthogonal, the are eigenvectors!
        \begin{align*}
          \E[x\tp{3}](\beta_h,\beta_h) 
            %&= \sum_{h'=1}^k \pi_{h'} (\beta_{h}^T \beta_{h'})^2 \beta_{h'} \\
            %&= \sum_{h'=1}^k \pi_{h'} \delta_{hh'} \beta_{h'} \\
            &= \pi_{h} \beta_{h}.
        \end{align*}
      \item<4-> In general, whiten $\E[x\tp{3}]$ first.
    \end{itemize}
  }{%
  }
  \begin{canvas}
    \point{mark}{(1cm,0)};
    \point{start}{(1cm,1cm)}; %{pic cs:gen} -| mark)};

    \drawgen{($(start) + (0,1cm)$)};
    \node[anchor=west] (diag) at ($(start) + (1cm,0.0cm)$) {%
      \includegraphics[width=0.45\textwidth,height=3cm,keepaspectratio]{figures/mog.pdf}
    };
    \uncover<2->{%
      \tensorfactorization{(-3cm,-2cm)};
    }
  \end{canvas}
\end{frame}

@@

  \begin{canvas}
    % Tasks.
    \drawgen{(-3cm,1cm)}
    \node[below=0.1cm of x.south] {Generative Models};

    % Highlight
    \draw<2>[scale=0.8,fill=green,opacity=0.4,dashed] (1cm,2.5cm) rectangle (6.5cm,-2.5cm);
      \drawdisc{(3cm,1cm)}
      \node[below=0.1cm of y.south] {Discriminative Models};

@@

  \splitcolumn{%
    \tikzmark{model}
    \begin{tikzpicture}
      \drawdisc{(0,0)}
    \end{tikzpicture}
    \begin{itemize}
      \item<2-> $h \sim \Mult([\pi_1, \pi_2, \cdots, \pi_k])$.
      \item<4-> $y = \beta_h^T x + \epsilon$.
    \end{itemize}
  }{%
  }
    \begin{canvas}
      % x, y
      \point{mark}{(0cm,0cm)}
      \point{model}{({pic cs:model} -| mark)}
      \node[anchor=west] at ($(model) + (0,-1cm)$) {%
      \includegraphics<1>[width=5cm,height=6cm,keepaspectratio]{figures/mlr-0.pdf}
      \includegraphics<2>[width=5cm,height=6cm,keepaspectratio]{figures/mlr-1.pdf}
      \includegraphics<3>[width=5cm,height=6cm,keepaspectratio]{figures/mlr-2.pdf}
      \includegraphics<4>[width=5cm,height=6cm,keepaspectratio]{figures/mlr-3.pdf}
      \includegraphics<5>[width=5cm,height=6cm,keepaspectratio]{figures/mlr-4.pdf}
      \includegraphics<6>[width=5cm,height=6cm,keepaspectratio]{figures/mlr-5.pdf}
      \includegraphics<7>[width=5cm,height=6cm,keepaspectratio]{figures/mlr-6.pdf}
        };
    \end{canvas}
\end{frame}

@@

  \begin{canvas}
    \node[anchor=east] (data) at (-2cm,0) {%
    \includegraphics[width=4cm,height=6cm,keepaspectratio]{figures/mlr-6.pdf}
    };

    % x, y
    \node[anchor=west,scale=1.0] (params) at (1.5cm,0) {%
      $\begin{bmatrix} \pi_1 \\ \pi_2 \\ \vdots \\ \pi_k \end{bmatrix}  
       \begin{bmatrix} 
                 &         &       &         \\
                 &         &       &         \\
         \beta_1 & \beta_2 & \dots & \beta_k \\
                 &         &       &         \\
                 &         &       &         
       \end{bmatrix} $
      };
    %\node[anchor=west,right=0.1cm of params] {%
    %\includegraphics[width=4cm,height=2cm,keepaspectratio]{figures/disc.png}
    %};

@@

  \splitcolumn{%
  \begin{align*}
    \action<1->{%
    y\tikzmark{regA} &= \mathmb{\ob{\innerp{\E[\beta_h]}{x}}^{\textrm{linear measurement}}} &&+ \mathmr{\ob{(\beta_h - \E[\beta_h])^T x + \epsilon}^{\textrm{noise}}} \\[4ex]
    }
    \action<2->{%
    y^2 \tikzmark{regB}
      &= \left(\innerp{\beta_h}{x} + \epsilon\right)^2 && \\
    }
    \action<3->{%
    &= 
    \color{blue}
      \robustaltm<3>{%
            \innerp{\E[\beta_h\tp{2}]}{x\tp{2}}
        }{%
          \ub{\innerp{\E[\beta_h\tp{2}]}{x\tp{2}}}_{M_2} 
        }
        &&+ \color{DarkGreen} \textrm{bias} + \color{red} \textrm{noise} \\[4ex]
    }
    \action<5->{%
    y^3 \tikzmark{regC}
    &= \color{blue} \ub{\innerp{\E[\beta_h\tp{3}]}{x\tp{3}}}_{M_3} &&+ \color{DarkGreen} \textrm{bias} + \color{red} \textrm{noise} 
    }
  \end{align*}
  }{%
  }
  \begin{canvas}
    \point{mark}{(3cm,0)};
    \uncover<1-> {%
      \regressionA{($({pic cs:regA} -| mark) + (0,-2.5cm)$)};
    }
    \uncover<3-> {%
      \regressionB{($({pic cs:regB} -| mark) + (0,-3cm)$)};
    }
    \uncover<5-> {%
      \regressionC{($({pic cs:regC} -| mark) + (0,-3cm)$)};
    }
  \end{canvas}

@@

\begin{frame}
  \frametitle{Recovering Parameters.}
  \centering

@@

  \begin{canvas}
    \uncover<2->{%
      \tensorfactorization{(-3cm,-2cm)};
    }
  \end{canvas}

@@

    \begin{align*}
      \robustaltm<-2>{\hat M_2}{\mathmb{\hat M_3}} &= \arg\min_{M} \sum_{(x,y)\in\mathcal{D}} \left(y^2 - 
      \robustaltm<-2>{\innerp{M}{x\tp{2}}}{\mathmb{\innerp{M}{x\tp{3}}}}
      - \textrm{bias}\right)^2 
      \uncover<2->{+
      \robustaltm<2>{\mathmb{\ub{\|M\|_{*}}_{\sum_i \sigma_i(M)}}}
        {\|M\|_{*}}
      } \\
    \end{align*}

  \begin{canvas}
    % x, y
    \alt<-2>{%
      \matrixfactorization{(-3cm,-2cm)}
    }{%
      \tensorfactorization{(-3cm,-2cm)}
    }
  \end{canvas}
\end{frame}

@@

  \begin{canvas}
    % x, y
    \node[anchor=west] (em) at (-6.5cm,-1.5cm) {%
      \includegraphics<1>[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3.png}
      \includegraphics<2>[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3-em.png}
      \includegraphics<3>[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3-spec.png}
      \includegraphics<4->[width=\textwidth,height=5cm,keepaspectratio]{figures/1-8-3-specm.png}
      };
    % x, y
    \node[anchor=west, right=6cm of em] at (em.west) {%
      \includegraphics[width=\textwidth,height=5cm,keepaspectratio]{figures/hist.png}
    };

@@

\begin{frame}
  \frametitle{On Initialization (Cartoon)}

  \begin{tikzpicture}
    % x, y
    \llhood{0}{0};

    \node<2->[scale=0.7] at (em2) {x};
    \node<2-> at ($(em2) + (0.6cm,0)$) {$\mathmr{\hat\theta_{\textrm{EM}}}$};
    \draw<2->[-latex,smooth,line width=1pt,red] ($(em2-start) + (+0.1cm,+0.05cm)$) -- ($(em2) + (+0.15cm,0.00cm)$);
    \draw<2->[dashed,red,line width=0.7pt] ($(em2)-(3.5cm,0)$) -- ($(em2)+(0.5cm,0)$);

    \draw<3>[latex-latex,DarkGreen,line width=1pt,dashed] ($(mle) + (-1.2cm,0.8cm)$) -- node[above]{$\mathmg{\epsilon}$} ($(mle) + (+1.2cm,0.8cm)$);
    \node<4->[scale=0.7] at (spec) {x};
    \node<4-> at ($(spec) + (0.5cm,0.3cm)$) {$\mathmg{\hat\theta_{\textrm{spec}}}$};
    \draw<4->[dashed,DarkGreen,line width=0.7pt] ($(spec)-(0.5cm,0)$) -- ($(spec)+(3.5cm,0)$);

    \draw<5->[-latex,smooth,line width=1pt,DarkGreen] ($(spec) + (-0.1cm,+0.05cm)$) -- ($(mle) + (-0.30cm,+0.10cm)$);
    %\node[scale=0.7] at (mle) {x};
    \node<5->[anchor=west] at ($(mle) + (0.3cm,0)$) {$\mathmb{\theta^*}_{\textrm{spec + EM}}$};

  \end{tikzpicture}
